\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip}
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\usepackage{supertabular,tabularx}
\usepackage{titlesec}
\usepackage{multicol,multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}

\begin{document}
\pagestyle{empty}

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Owen Brock} \\[7.5pt]
\href{mailto:obrock@uncc.edu}{\raisebox{-0.05\height}\faEnvelope \ obrock@uncc.edu} \ $|$ \ 
\href{https://linkedin.com}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \ 
\href{https://github.com}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
\href{tel:+19842324887}{\raisebox{-0.05\height}\faMobile \ +(984) 232-4887} \\
\end{tabularx}

\section{Education}
\textbf{The University Of North Carolina at Charlotte} \hfill Aug 2022 – May 2026 \\
B.S. in Computer Science \\
GPA: \textit{3.7}
\begin{itemize}[noitemsep]
    \item \textbf{Relevant Coursework:} Data Structures and Algorithms, Database Design \& Implementation, Web App Design and Development, Logic and Algorithms
\end{itemize}


\section{Experience}

\textbf{TalkNex}, Software Applications \hfill Jan 2024 - Present
\begin{itemize}[noitemsep]
    \item Developed a user-friendly WebRTC application using HTML, CSS, and JavaScript, representing a versatile solution for efficient online collaboration.
    \item Enables seamless real-time video conferencing and collaboration among users from any compatible web browser.
\end{itemize}

\textbf{HackNC}, Participant \hfill Fall 2023
\begin{itemize}[noitemsep]
    \item Developed "LingoAlly," an app to assist non-native language speakers in forming local communities.
    \item Used Expo Dev to create a universal native app with GPT-3 embedded
    \item Won 2nd place in overall judging
\end{itemize}

\textbf{Ufit Tracker}, Software Applications \hfill Feb 2024 - Present
\begin{itemize}[noitemsep]
    \item Designed a website for UNC Charlotte students to enhance their gym experience through workout tracking, goal setting, and community features.
    \item Built interactive UI components providing an engaging experience, allowing users to keep input through localStorage.

\end{itemize}

\section{Involvement}

\textbf{Charlotte Hack} \hfill Sep 2023 – Present
\begin{itemize}[noitemsep]
    \item Collaborated on technology improvement projects and engaged in industry events, enhancing problem-solving skills and tech understanding.
\end{itemize}

\textbf{Missing Maps} \hfill Aug 2023 – Present
\begin{itemize}[noitemsep]
    \item Contributed to creating maps for vulnerable communities in Central Europe, utilizing Java OpenStreetMap Editor for disaster preparation.
\end{itemize}

\textbf{Web Wizard}, Fraternity Website Development \hfill April 2023 – Present
\begin{itemize}[noitemsep]
    \item Led the development and maintenance of the fraternity's website, focusing on responsive design and user engagement.
\end{itemize}

\section{Skills}
\textbf{Programming Languages:} Python, Java, JavaScript, SQL \\
\textbf{Tech Stack/Frameworks:} Next.js, React-Native, React.js \\
\textbf{Other Skills:} Git, Docker, MySQL, Latex

\vfill
\center{\footnotesize Last updated: \today}

\end{document}
